Magic Vs Evolution

### 2024-04-03 paper/paper.qmd
commiting changes

---
title: "Magic Vs Evolution"
subtitle: "Or more specifically language in Harry Potter vs Darwin's Natural Selection"
author: "Shreya Sakura Noskor"
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

darwin_reduced <- darwin |>
  filter(!is.na(text)) |> 
  mutate(natural_count = str_count(text, regex('natural', ignore_case = T)), 
         magic_count = str_count(text, regex('magic|miracle', ignore_case = T)), 
         word_count = str_count(text, "\\w+"))

write_csv(darwin_reduced, "../data/analysis_data/darwin_reduced.csv")
arrow::write_parquet(darwin_reduced, "../data/analysis_data/darwin_reduced.parquet")
```

@@

@@

@@

Define $y_i$ is the number of times "natural" appeared in the text and the explanatory variable is the number of words in the line.

@@

saveRDS(
  darwin_nature,
  file = "../models/darwin_nature.rds"
)
```

```{r}
#| echo: false
#| warning: false
#| message: false
plot_predictions(darwin_nature, condition = "word_count") +
  labs(x = "Number of words",
       y = "Average number of \"natural\"s in the first 10 lines") +
  theme_classic()
```
Negative relation it seems

@@

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

saveRDS(
  darwin_magic,
  file = "../models/darwin_magic.rds"
)
```

@@

@@

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

>>>>

---
title: "Magic Vs Evolution"
subtitle: "Or more specifically language in Harry Potter vs Darwin's Natural Selection"
author: "Shreya Sakura Noskor"
thanks: "Code and data are available at: [HarryDarwin](https://github.com/NotSakura/HarryDarwin.git)"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
header-includes:
  - \usepackage{float} 
  - \floatplacement{table}{H}
number-sections: true
include-in-header: 
  text:
    \renewcommand{\abstractname}{Abstract}
bibliography: references.bib
toc: true
---

@@

harry <- read_csv(
  "../data/raw_data/harry.csv",
  col_types = cols(
    page_num = col_integer(),
    text = col_character()
  )
)

darwin_reduced <- darwin |>
  filter(!is.na(text)) |> 
  mutate(natural_count = str_count(text, regex('natural|species', ignore_case = T)), 
         magic_count = str_count(text, regex('magic|miracle', ignore_case = T)), 
         word_count = str_count(text, "\\w+"))

write_csv(darwin_reduced, "../data/analysis_data/darwin_reduced.csv")
arrow::write_parquet(darwin_reduced, "../data/analysis_data/darwin_reduced.parquet")

harry_reduced <- harry |>
  filter(!is.na(raw_text)) |> 
  mutate(natural_count = str_count(raw_text, regex('natural|species', ignore_case = T)), 
         magic_count = str_count(raw_text, regex('magic|miracle', ignore_case = T)), 
         word_count = str_count(raw_text, "\\w+"))

write_csv(darwin_reduced, "../data/analysis_data/harry_reduced.csv")
arrow::write_parquet(darwin_reduced, "../data/analysis_data/harry_reduced.parquet")

@@

Research Question: Does the topic we talk about influence our language, or does the laguage influence the theme of the topic.

@@

## Source
The data utilized was from Project Gutenburg and PDF Drives and with the help of R [@citeR] we were able to create this paper. Also code for making the models were made referencing Telling Stories by Rohan Alexander[@rohan]. Other R packages were used to clean, process and model the data such as, @tidy, @gut, @rstanarm, @pdf, @dplyr, @arrow, @stringr, @marginaleffects.

## Variables

### Distribution of each word with each text

@@

Define $y_i$ is the number of times "natural" appeared in each text and the explanatory variable is the number of words in the line. We predict to see that there is a positive correlation in Darwin's text but not in Harry Potter due to the difference in topics.

@@

saveRDS(
  darwin_nature,
  file = "../models/darwin_nature.rds"
)

harry_nature <-
  stan_glm(
    natural_count ~ word_count,
    data = harry_reduced,
    family = poisson(link = "log"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )

saveRDS(
  harry_nature,
  file = "../models/harry_nature.rds"
)
```

```{r}
#| echo: false
#| warning: false
#| message: false
plot_predictions(darwin_nature, condition = "word_count") +
  labs(x = "Number of words",
       y = "Average number of \"natural\"s in the first 10 lines") +
  theme_classic()
```
positive correlation it seems

```{r}
#| echo: false
#| warning: false
#| message: false
plot_predictions(harry_nature, condition = "word_count") +
  labs(x = "Number of words",
       y = "Average number of \"natural\"s in the first 10 lines") +
  theme_classic()
```
No correlation at all

@@

We predict to see that there is a positive correlation in Darwin's text but not in Harry Potter due to the difference in topics.

@@

saveRDS(
  darwin_magic,
  file = "../models/darwin_magic.rds"
)

harry_magic <-
  stan_glm(
    magic_count ~ word_count,
    data = harry_reduced,
    family = poisson(link = "log"),
    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
    seed = 853
  )

saveRDS(
  harry_magic,
  file = "../models/harry_magic.rds"
)
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
plot_predictions(harry_magic, condition = "word_count") +
  labs(x = "Number of words",
       y = "Average number of \"magic\"s or \"miracle\"s appearing") +
  theme_classic()
```

@@

We predict to see that there is a positive correlation in Harry Potter but not in Darwin's text due to the difference in topics.

@@

darwin_nature <-
  readRDS(file = "../models/darwin_nature.rds")

darwin_magic <-
  readRDS(file = "../models/darwin_magic.rds")

harry_nature <-
  readRDS(file = "../models/harry_nature.rds")

harry_magic <-
  readRDS(file = "../models/harry_magic.rds")
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-darwin_nature
#| tbl-cap: "Model Summary showcasing the correlation coeffcient for Darwin's evolution book and the word nature"
#| warning: false

modelsummary::modelsummary(
  list(
    "darwin and nature" = darwin_nature
  ),
  statistic = "mad",
  fmt = 2
)
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-darwin_magic
#| tbl-cap: "Model Summary showcasing the correlation coeffcient for Darwin's evolution book and the word magic"
#| warning: false

modelsummary::modelsummary(
  list(
    "darwin and magic" = darwin_magic
  ),
  statistic = "mad",
  fmt = 2
)
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-harry_nature
#| tbl-cap: "Model Summary showcasing the correlation coeffcient for  Harry Potter and The Prisoner of Azkaban and the word nature"
#| warning: false

modelsummary::modelsummary(
  list(
    "harry and nature" = harry_nature
  ),
  statistic = "mad",
  fmt = 2
)
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-harry_magic
#| tbl-cap: "Model Summary showcasing the correlation coeffcient for Harry Potter and The Prisoner of Azkaban and the word magic"
#| warning: false

modelsummary::modelsummary(
  list(
    "harry and magic" = harry_magic
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

## Why is the result the way it is {#sec-first-point}

## Importance
